### 2015-11-06 CVPR16/Source/applications.tex
Fixed the contBBoxModel.tex
changes
edit Sec 4.2

We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates its versatility. Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -Z 
   + \sum_{t=s_i}^{e_i} \WpEnergy{track}
  \\
  + 
  \sum_{t=s_i}^{e_i}
  \sum_{i=1}^N  
  \left( 
  \WEnergy{detect}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace,
\end{multline}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights and $Z$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modelling for point track and bounding box energies; please refer to our supplementary material for the formulations of other energies.

\begin{figure}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
    \input{Source/scenelayoutoverlayCity0961} \\
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each car are modeled as random variables. (Bottom) Graphical model for a single frame. The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables (detection bounding boxes and point tracks), while the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{figure}

@@

For an object $i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\input{contBBoxModel.tex}
%\input{Source/squareBBoxModel.tex}

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to the supplementary material for the
comparison of inference methods.

>>>>

We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -Z 
   + \sum_{t=s_i}^{e_i} \WpEnergy{track}
  \\
  + 
  \sum_{t=s_i}^{e_i}
  \sum_{i=1}^N  
  \left( 
  \WEnergy{detect}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace,
\end{multline}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $Z$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modelling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary.

\begin{figure}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each car are modeled as random variables. (Bottom) Graphical model for a single frame. The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables (detection bounding boxes and point tracks), while the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{figure}

@@

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\input{Source/contBBoxModel}
%\input{Source/squareBBoxModel.tex}

@@

\subsubsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to the supplementary material for the
comparison of inference methods.

### 2015-11-06 CVPR16/Source/contBBoxModel.tex
edit Sec 4.2

Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded assuming
the point is on object $i$ with mean depth $\meandepth{i}$ as
\begin{align}
  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
\end{align}

>>>>

Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let the 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$ as
\begin{align}
  O_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
\end{align}
